---
title: "Subsetting Data CH2"
author: "S Richard Smith"
date: "February 7, 2016"
output: html_document
---

# Subsetting Data

## The Dataset

I've chosen to work with the dataset from the UCI Machine Learning Repository on Bank Marketing Data (found [here](https://archive.ics.uci.edu/ml/datasets/Bank+Marketing#)).

The data is from a Portugese banking institution. It captures information about a marketing campaign they undertook.

The data is stored in several formats. I used the most complete data set as a starting point ([bank-additional-full.csv](https://www.dropbox.com/s/732hq892axmrk49/bank-additional-full.csv?dl=0)).


## Dataset Summary

Using R, I loaded the data from the file.

```{r}
BankDat <- read.csv(file = 'C:/CUNY/Class Material/Github/Subsetting-Datasets-607ch2/bank-additional/bank-additional-full.csv',header = TRUE,sep = ";",quote = "\"",dec = ".",row.names = NULL)
```

Doing some summary analysis, I discovered the following:

* The data has the following number of rows and columns:
```{r}
dim(BankDat)
```

* The data has the following fields:
```{r}
names(BankDat)
```


## The Scenario

I am simulated a question from a colleague about whether or not the survey is representative of our banking customer base at large. As such, I need a subset of the data that includes only the demographic information from the full data set. I used the following to generate that subset and did the same summary review as above plus a more detailed look by field:

```{r}
BankDatSub<-BankDat[,1:8]
```

* Dimensions
```{r}
dim(BankDatSub)
```

* Field Names
```{r}
names(BankDatSub)
```

* Summary by field
```{r}
summary(BankDatSub)
```